Introduction to LLL\\``Cryptography''

### 2021-05-25 paper.tex
add lattice introductions

\newtheorem{definition}{Definition}[section]
\newcommand{\R}{\mathbb{R}}
\newcommand{\dd}{\cdot}

@@

Taken a set of linearly independent vectors $x = (v_1,\ldots,v_n) \in V$ we say that $x$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write

@@

@@

>>>>

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{property}{Property}[section]
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\dd}{\cdot}

@@

Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write

@@

If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \texttt{orthonormal}.

\begin{theorem}
    \textbf{Gram-Schmidt Algorithm}
\end{theorem}

Let $b = (v_1, \ldots, v_n)$, be a basis for a vector space $V \subset \R^m$. There is an algorithm to create an orthogonal basis
$b^* = (v_1^*,\ldots,v_n^*)$.
The two bases have the property that Span$\{v_1,\ldots,v_i\}$ = Span$\{v_1^*,\ldots,v_i^*\}$ for all $i = 1,2,\ldots,n$

@@

\begin{definition}
    \textbf{Lattice}
\end{definition}

Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \texttt{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
all integer linear combinations of $v_1,\ldots,v_n$.

\begin{center}
    $L = \bigg\{\sum_{i=1}^{n} a_iv_i, a_i \in \Z \bigg\}$
\end{center}

If $v_i$ for every $i = 1,\ldots\,n$ has integer coordinates then the lattice is
called \texttt{Integral Lattice}.

On the figure \ref{fig:lattice1} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$:

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.7\textwidth]{./img/lattice.png}
    \caption{Lattice spanned by $v, w$}
    \label{fig:lattice1}
\end{figure}
